AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-28 Paper/main.tex
10-28 paper

Next,

\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
    \caption{wait2write}\label{fig:heatmap}
\end{figure}

>>>>

The second question we want AttCRISPR to answer is why it give two low scores at position 14 and 16. 
In practice, we will try to answer this question with second-order preference. 
Let AttCRISPR output the second-order preference matrix $B$ corresponding to the source sgRNA, and show it in Figure~\ref{fig:heatmap}. 
It is obvious that a few unusual bright spots appear in the red box in Figure~\ref{fig:heatmap}. 
We believe that tells us the nucleotide at position 15 has a great effect on the score of position 14 andd 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.

\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
    \caption{The visualization of second-order preference matrix $B$, 
the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
The warmer the color, the more important it is. 
In the red box, a few unusual bright spots appear. 
To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
}\label{fig:heatmap}
\end{figure}
